### 2016-11-04 introduction.tex
more shit

Essentially, \cite{mozer1989using} observed that the behavior of neural networks during training is not to distribute the learning representation evenly or even equitably across hidden units. What actually happens is that a few, elite neurons learn an approximation of the input-output function, and the remaining units simply learn a complex interdependence function which cancels out their respective influence. Furthermore, assuming enough units exist to learn the function in question, increasing the number of parameters does not increase the richness or robustness of the learned approximation, but rather simply increases the number of noisy parameters to cancel. This is evinced by the fact that in many cases, whole neurons can be removed from a network with minimal to no impact on the output approximation, and even more so in the case of networks with copious extraneous units. In other words, there are few bipartisan units in a trained network. A unit is typically either part of the input-output function approximation, or it is part of an elaborate noise cancellation task force. Assuming this is true, most of the compute-time spent training a neural network is likely occupied by this arguably wasteful procedure of silencing superfluous parameters, and pruning is thus a necessary treatment procedure to ``trim the fat.''

>>>>

Essentially, \cite{mozer1989using} observed that the behavior of neural networks during training is not to distribute the learning representation evenly or even equitably across hidden units. What actually happens is that a few, elite neurons learn an approximation of the input-output function, and the remaining units simply learn a complex interdependence function which cancels out their respective influence. Furthermore, assuming enough units exist to learn the function in question, increasing the number of parameters does not increase the richness or robustness of the learned approximation, but rather simply increases the number of noisy parameters to be canceled during training. This is evinced by the fact that in many cases, whole neurons can be removed from a network with minimal to no impact on the output approximation, and even more so in the case of networks with copious extraneous units. In other words, there are few bipartisan units in a trained network. A unit is typically either part of the input-output function approximation, or it is part of an elaborate noise cancellation task force. Assuming this is true, most of the compute-time spent training a neural network is likely occupied by this arguably wasteful procedure of silencing superfluous parameters, and pruning is thus a necessary treatment procedure to ``trim the fat.''
